\section{Introduction}
It is a tedious job to measure material properties of all materials, for
there are infinitely many; Let the temperature-dependency for all of them, etc.
Let us learn from e.g. engineers who had to predict whether a bridge design
would collapse, or whether an ocean protection barrier would hold.
Back in the days, they would build a scaled-down model and use that
prototype to provide an answer. Nowadays, they are able to use the computer to
simulate the situations in far less time and with far more accuracy than they
were used to be able.

The power of the computer may be used in material sciences as well. We may, for
example, compute the diffusion coefficient numerically, rather than measuring
it.

Verlet (1967) \cite{verlet:firstPaper} was one of the pioneers in this area.
While his simulations had to run for days, our simulations may run for several
minutes, allowing us to simulate far more details.

In my molecular dynamics simulation (MDS), I will redo some of Verlet's work to
validate my simulation. The material under consideration is Argon. I will look
at properties like the pair-correlation function, pressure, diffusion,
parallelisation of the algorithm and phase-transitions.




% The \textit{proceedings} are the records of a conference.
% ACM seeks to give these conference by-products a uniform,
% high-quality appearance.  To do this, ACM has some rigid
% requirements for the format of the proceedings documents: there
% is a specified format (balanced  double columns), a specified
% set of fonts (Arial or Helvetica and Times Roman) in
% certain specified sizes (for instance, 9 point for body copy),
% a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
% the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
% and (1.9 cm [.75"]) left and right; specified column width
% (8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
% 
% The good news is, with only a handful of manual
% settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
% and {\texttt{\char'134 alignauthor}} commands, you have
% already used; another, {\texttt{\char'134 balancecolumns}}, will
% be used in your very last run of \LaTeX\ to ensure
% balanced column heights on the last page.}, the \LaTeX\ document
% class file handles all of this for you.
% 
% The remainder of this document is concerned with showing, in
% the context of an ``actual'' document, the \LaTeX\ commands
% specifically available for denoting the structure of a
% proceedings paper, rather than with giving rigorous descriptions
% or explanations of such commands.